Covid-19 Fields Survey Data Protocol

### 2023-01-26 protocol/Background_and_methods_Jan_24.qmd
updated

@tbl-model shows the results of the logistic regression on vaccination status using socio-economic, geographical factors (by Health Region) and their interactions as predictors. The reference groups in each case were set as follow:  16 to 24 years (age group), White Caucasian (Race), Toronto (Health Region), Over CAD 90,000 (Income). Socio-economic factors with statistically significant odds ratios were the age group of 65 years and over (OR=0.58), persons who identified as Arab/Middle Eastern (OR=0.15), Black (OR=0.17), Indigenous (OR=0.27), Latin American (OR=0.24), South Asian (OR=0.17) and Other Race/Ethnicity (a group  that included minorities not found elsewhere, OR=0.17), and those that lived in a household with an income bracket between CAD 25,000 and CAD 39,999.

Regarding the interaction of socio-economic and geographical factors, statistically significant odds ratios were the Central Health Region and Income of 15000 to 24999 CAD (OR=0.4), Age Group of 65 years and older with a household income between 25000 and 39999 CAD (OR=0.001), and with an income between 40000 and 59999 (OR=3.12)

>>>>

@tbl-model shows the results of the logistic regression on vaccination status using socio-economic, geographical factors (by Health Region) and their interactions as predictors. The reference groups in each case were set as follows:  16 to 24 years (age group), White Caucasian (Race), Toronto (Health Region), Over CAD 90,000 (Income). Socio-economic factors with statistically significant odds ratios were the age group of 65 years and over (OR=0.58), persons who identified as Arab/Middle Eastern (OR=0.15), Black (OR=0.17), Indigenous (OR=0.27), Latin American (OR=0.24), South Asian (OR=0.17) and Other Race/Ethnicity (a group  that included minorities not found elsewhere, OR=0.17), and those that lived in a household with an income bracket between CAD 25,000 and CAD 39,999.

Regarding the interaction effects, the interaction of the Central Health Region and income bracket between 15000 to 24999 CAD was statistically significant (OR=0.4). In the age group and income interaction effect, significant effects were estimated for those 65 years and older with a household income between 25000-39999 CAD (OR=0.001), and with an income between 40000 and 59999 (OR=3.12). In the case of race and income, significant effects were estimated for individuals that identified as Arab/Middle Easterners with a family income between 15000 and 24000 (OR=5.68) or income under 15000 CAD (OR=4.21), Black individuals with a family income under 15000 CAD (OR=4.26) or between 15000 and 24999 CAD (OR=3.35); additionally, there were statistically significant interaction effects in the case of those that identified as belonging to a race not identified elsewhere with an income under 15000 CAD (OR=3.73), between 15000 and 24999 (OR 11.2), between 25000 and 39999 CAD (OR=4.67), or with an income between 40000 and 59999 CAD (OR=9.58). Finally, there was also a significant interaction effect for South Asian individuals with an income under 15000 CAD (OR=3.10).

### 2023-01-26 protocol/Background_and_methods_Jan_24.tex
updated

\title{Covid-19 Fields Survey Data Protocol}
\author{Ariel Mundo Ortiz}
\date{1/24/23}

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, boxrule=0pt, enhanced, breakable, frame hidden]}{\end{tcolorbox}}\fi

@@

Table~\ref{tbl-model} shows the results of the logistic regression on
vaccination status using socio-economic, geographical factors (by Health
Region) and their interactions as predictors. The reference groups in
each case were set as follow: 16 to 24 years (age group), White
Caucasian (Race), Toronto (Health Region), Over CAD 90,000 (Income).
Socio-economic factors with statistically significant odds ratios were
the age group of 65 years and over (OR=0.58), persons who identified as
Arab/Middle Eastern (OR=0.15), Black (OR=0.17), Indigenous (OR=0.27),
Latin American (OR=0.24), South Asian (OR=0.17) and Other Race/Ethnicity
(a group that included minorities not found elsewhere, OR=0.17), and
those that lived in a household with an income bracket between CAD
25,000 and CAD 39,999.

Regarding the interaction of socio-economic and geographical factors,
statistically significant odds ratios were the Central Health Region and
Income of 15000 to 24999 CAD (OR=0.4), Age Group of 65 years and older
with a household income between 25000 and 39999 CAD (OR=0.001), and with
an income between 40000 and 59999 (OR=3.12)

>>>>

\title{Covid-19 Fields Survey Data Protocol}
\author{Ariel Mundo Ortiz}
\date{1/25/23}

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, enhanced, breakable, boxrule=0pt, frame hidden]}{\end{tcolorbox}}\fi

@@

Table~\ref{tbl-model} shows the results of the logistic regression on
vaccination status using socio-economic, geographical factors (by Health
Region) and their interactions as predictors. The reference groups in
each case were set as follows: 16 to 24 years (age group), White
Caucasian (Race), Toronto (Health Region), Over CAD 90,000 (Income).
Socio-economic factors with statistically significant odds ratios were
the age group of 65 years and over (OR=0.58), persons who identified as
Arab/Middle Eastern (OR=0.15), Black (OR=0.17), Indigenous (OR=0.27),
Latin American (OR=0.24), South Asian (OR=0.17) and Other Race/Ethnicity
(a group that included minorities not found elsewhere, OR=0.17), and
those that lived in a household with an income bracket between CAD
25,000 and CAD 39,999.

Regarding the interaction effects, the interaction of the Central Health
Region and income bracket between 15000 to 24999 CAD was statistically
significant (OR=0.4). In the age group and income interaction effect,
significant effects were estimated for those 65 years and older with a
household income between 25000-39999 CAD (OR=0.001), and with an income
between 40000 and 59999 (OR=3.12). In the case of race and income,
significant effects were estimated for individuals that identified as
Arab/Middle Easterners with a family income between 15000 and 24000
(OR=5.68) or income under 15000 CAD (OR=4.21), Black individuals with a
family income under 15000 CAD (OR=4.26) or between 15000 and 24999 CAD
(OR=3.35); additionally, there were statistically significant
interaction effects in the case of those that identified as belonging to
a race not identified elsewhere with an income under 15000 CAD
(OR=3.73), between 15000 and 24999 (OR 11.2), between 25000 and 39999
CAD (OR=4.67), or with an income between 40000 and 59999 CAD (OR=9.58).
Finally, there was also a significant interaction effect for South Asian
individuals with an income under 15000 CAD (OR=3.10).
